Improving phase-matching of FWM with temperature

### 2015-09-15 latex/article.tex
introduction

\cleardoublepage 
\section{Introduction}
\subsection{Motivation}
\subsection{Partially degenerate Four-Wave Mixing}
Four-Wave Mixing (FWM) is a nonlinear optical effect

****
\section{Linear optics}

@@

\section{Non-linear optics}
A nonlinear dielectric medium is characterized by a nonlinear relation between P and E, such as
$$\textbf{P} = \varepsilon_0 \left( \chi^{(1)} \cdot \textbf{E} + \chi^{(2)} : \textbf{E}^2 + \chi^{(3)} \vdots \textbf{E}^3 + \cdots \right) $$
In everyday condition linear effects are much larger than nonlinear ones.
The relation between $\mathrm{P}$ and $\mathrm{E}$ becomes nonlinear when $\mathrm{E}$ has a value comparable to interatomic electric fields, which are typically $\sim 10^5-10^8$ \si{\V\per\m}.

>>>>

\cleardoublepage 
\section{Introduction}
\subsection{Motivation}
In my scholastic career I approached the study of optics in an elective course of my third year of undergraduate academic degree.
I became very interested in the subject, in particular because of the potential developement of photonics for communication and computing.
I discussed different topics with the professors and some researchers.
One of them suggested me a few interesting topics in guided-wave optics which could be studied as a undergraduate thesis.

I choose to study the the temperature behaviour of silicon waveguides.
The reason of the choice is that there are always discrepancies between the design of silicon objects and their actual production by the factory.
The aim of the study is to exploit this behaviour to correct possible production defects of the materials.

The study is focused on a silicon-based waveguide with rectangular section with a silicon ($\mathrm{Si}$) core and a silica ($\mathrm{Si0}_2$) cladding.
Its purpose is to generate light through a partial degenerate Four-Wave Mixing phenomenon

\subsection{Partially degenerate Four-Wave Mixing}
Four-Wave Mixing (FWM) is a nonlinear optical effect due to the susceptibility of silicon.
Silicon is an isotropic material and therefore second order susceptibility $\chi^{(2)}$ (almost) vanishes.
Third order susceptibility $\chi^{(3)}$, on the other hand, is not zero and is responsible among the other effects for FWM, which is indeed a third order phenomenon.

In general FWM implies the mix of four waves of different frequency.
Partial degenerate FWM, instead, is a specific case in which two waves have the same frequency.
Therfore it is about two waves (pump and signal) which generate a third wave (idler).

\section{Linear optics}

@@

photos?
\section{Non-linear optics}
A nonlinear dielectric medium is characterized by a nonlinear relation between P and E, such as
$$\textbf{P} = \varepsilon_0 \left( \chi^{(1)} \cdot \textbf{E} + \chi^{(2)} : \textbf{E}^2 + \chi^{(3)} \vdots \textbf{E}^3 + \cdots \right) $$
In everyday condition linear effects are much larger than nonlinear ones.
The relation between $\mathrm{P}$ and $\mathrm{E}$ becomes nonlinear when $\mathrm{E}$ has a value comparable to interatomic electric fields, which are typically $\sim 10^5-10^8$ \si{\V\per\m}.
